Jahn-Teller effect with rigid octahedral rotations in perovskites

### 2023-09-28 manuscript/paper.tex
minor typos

Of course, beside the crystal field we consider in our simplistic model,
in real materials,
 there would be other local effects like
electronic correlations (Hubbard and Hund's interaction), 
and spin-orbit interaction, 
as well as band structure effects arising from
the electron hopping between the B ions.
The interplay between these and the crystal field (or JT) effect 
we discussed in this manuscript is also an interesting future work.

>>>>

Of course, beside the crystal field we consider in our simplistic model,
in real materials,
 there would be other local effects like
electronic correlations (Hubbard and Hund's interaction)
and spin-orbit interaction, 
as well as band structure effects arising from
the electron hopping between the B ions.
The interplay between these and the crystal field (or JT) effect 
we discussed in this manuscript is also an interesting future work.
